A parametric system for generating contour parallel toolpaths with adaptive extrusion width

### 2019-08-23 10_applications.tex
make applciations a subsection of discussion

\section{Applications}
Because under- and overfill regions affect narrow parts more than wide parts, the use cases for this algorithm are centered around objects which contain thin parts.
Although the algorithm improves performance for all parts compared to existing techniques, the enhancement is percentually larger for thin parts.

>>>>

\subsection{Applications}
Because under- and overfill regions affect narrow parts more than wide parts, the use cases for this algorithm are centered around objects which contain thin parts.
Although the algorithm improves performance for all parts compared to existing techniques, the enhancement is percentually larger for thin parts.
